\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-03-09 paper/main.tex

\todo[inline]{Describe/add the CV results here.}
\begin{itemize}
	\item 
\end{itemize}
We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC/MacroAUC} and $MicroAUC_p$) and evaluate them on in 5-fold protein split cross validation on the Yamanishi benchmark dataset to avoid validation overfitting and yield more realistic testing results. To evaluate the influence of the different
features separately, and determine whether they ``localize'' on the
PPI graph (and therefore can be exploited successfully by the graph
neural networks), we train and evaluate models with different types of
features, and with and without inclusion of the PPI graph,
separately, comparing the molecular (MolPred) and phenotype based (OntoPred) predictor and a combination of both, concatenating both features.
Table \ref{tab:STITCHresults} shows the results of these experiments.

We find that the model using ontology-based features
(\textit{OntoPred}) is showing better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in
increased performance when incorporating the PPI graph. This increase
can be observed with different graph neural network
architectures and configurations. While the {\em GCNConv} and
{\em GENConv} architecture already shows some minor improvement, the
\textit{ResGraphConv} blocks add a large amount of additional
learnable parameters to the network, leading to more expressive
power. To test whether the improvement is due to the number of
learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are
removed, resulting in a non--graph model. This pruned network, with
no information on the protein--protein interactions, reached very
similar results to the original \textit{OntoPred} model\todo{data
  not shown; and details missing from Methods} and showed no
improvement.

>>>>

We trained, validated and finally tested all considered models on the
STITCH dataset using a 5-fold cross-validation over a protein
split; we then selected the best-performing models (with respect to
\textit{AUROC/MacroAUC} and $MicroAUC_p$) and evaluate them on in 5-fold protein split cross validation on the Yamanishi benchmark dataset to avoid validation overfitting and yield more realistic testing results. To evaluate the influence of the different
features separately, and determine whether they ``localize'' on the
PPI graph (and therefore can be exploited successfully by the graph
neural networks), we train and evaluate models with different types of
features, and with and without inclusion of the PPI graph,
separately, comparing the molecular (MolPred) and phenotype based (OntoPred) predictor and a combination of both, concatenating both features.
Table \ref{tab:STITCHresults} shows the results of these experiments.

We find that the model using ontology-based features
(\textit{OntoPred}) is showing better performance on STITCH compared
to using only molecular features. We also observe that only the model
using ontology-based features results in increased performance when
incorporating the PPI graph. This increase can be observed with
different graph neural network architectures and configurations. While
the {\em GCNConv} and {\em GENConv} architecture already shows some
minor improvement, the \textit{ResGraphConv} blocks add a large amount
of additional learnable parameters to the network, leading to more
expressive power. To test whether the improvement is due to the number
of learnable parameters added or the result of better exploiting the
information about PPIs, we experiment with a graph model in which all
graph convolutional neural layers in the residual blocks are removed,
resulting in a non--graph model. This pruned network, with no
information on the protein--protein interactions, reached very similar
results to the original \textit{OntoPred} model and showed no
improvement.
